A thesis draft

### 2018-11-21 res/sections/10-ProjectAnalysis.tex

\item \textbf{VNFs} this are the core components that perform packets
  manipulation. This components are design to be lightweight services able to
  elaborate a great amount of packets per seconds. Manipulation can be of two
  typologies: stateful or stateless. In the first case, a state is maintained,
  and the VNF can perform heuristics about data coming through it (especially
  useful to detect patterns in the data flow, e.g. DDos attacks). In the second
  case, no state is maintained, and every packet is treated without any
  particular assumption. Following the RFC 7665, the VNF are also called Service
  Function (SF)\footnote{From now on the two terminologies will be use in a
    interchangeable way.}. \todo{Add ref to chap about SFC?}

>>>>

\item \textbf{VNFs} this are the core components that perform packets
  manipulation. This components are design to be lightweight services able to
  elaborate a great amount of packets per seconds. Manipulation can be of two
  typologies: stateful or stateless. In the first case, a state is maintained,
  and the VNF can perform heuristics about data coming through it (especially
  useful to detect patterns in the data flow, e.g. DDos attacks). In the second
  case, no state is maintained, and every packet is treated without any
  particular assumption. Following the RFC 7665, the VNF are also called Service
  Function (SF)\footnote{From now on the two terminologies will be use in a
    interchangeable way~\cite{medhat2017service}.}.
  \todo{Add ref to chap about SFC?}
